%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Senior Cloud Systems Developer Lead} % Job title
{Cloudreach} % Organization
{New York, NY} % Location
{Aug. 2017 --- Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed and implemented AWS based solutions for customers}
    \item {Guided team members to success with coaching and technical support}
    \item {Led technical discussions with customers to arrive at the appropriate solution for their use case}
    \item {Delivered robust, scalable technical solutions on time and under budget}
    \item {Explained work performed to customers in a clear, easy to digest manner, with accompanying documentation}
  \end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {Cloud Systems Developer} % Job title
    {Cloudreach} % Organization
    {New York, NY} % Location
    {Nov. 2014 --- Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented AWS EC2 based solutions for customer applications}
        \item {Migrated customer application data, databases, and workloads into AWS}
        \item {Integrated with customer technical teams to accelerate migration projects}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {OFILG Team Leader} % Job title
    {UNH-IOL (University of New Hampshire InterOperability Laboratory)} % Organization
    {Durham, NH} % Location
    {April 2012 --- Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of undergraduate students to conduct interoperability testing for member companies in the RDMA technology space.}
        \item {Maintained cluster of 30+ CentOS Linux nodes for testing and development purposes. Upgraded Operating Systems, packages, and hardware. Provisioned VPN users, racked and stacked servers, and maintained inventory.}
        \item {Hosted semi-annual "Debug Events" attended by member company representatives with the goal of fostering interoperability and open communication between competing companies.}
        \item {Spoke at 2013 IBUG Workshop on testing efforts and methodologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Interoperability Technician} % Job title
    {UNH-IOL (University of New Hampshire InterOperability Laboratory)} % Organization
    {Durham, NH} % Location
    {Oct. 2010 --- April 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tested interoperability of Fast Ethernet products for member companies.}
        \item {Moved into Autonegotiation subgroup to specialize in 802.3 Clause 28 conformance testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
